Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-01-19 manuscript/HIAs.qmd
add figure to ms

```{r setup, warning=F, message=F, include=F}
library(tidyverse)
library(knitr)
library(sf)
library(tmap)
library(stars)
library(terra)
```

@@

```{r}
naturetypes <- readRDS("../data/surveyData.RDS")
```

@@

tmap_arrange(positionMap, muniPlot,
             widths = c(.4, .6))
```

@@

![Schematic workflow followed in this paper. Sub-index A is calculated using spatially explicit aggregation (i.e .a simple overlay taking the mean value).](../images/workflow.jpg){#fig-workflow alt="Schematic workflow followed in this paper. Sub-index A is calculated using spatially explicit aggregation (i.e .a simple overlay taking the mean value)."}

We chose three municipalities in Norway to test out the indicator (FIG).
These municipalities are spread over xxx km north to south, and also differ in the amount of mire area, the total area surveyed, and the prevalence of infrastructure (TABLE)

>>>>

```{r setup, warning=F, message=F, include=F}
#| warning: false
#| message: false
#| include: false
#| eval: true

library(tidyverse)
library(knitr)
library(sf)
library(tmap)
library(stars)
library(terra)
```

@@

```{r}
# read cached rds file
naturetypes <- readRDS("../data/surveyData.RDS")
```

@@

methodsMap <- tmap_arrange(positionMap, muniPlot,
             widths = c(.4, .6))

tmap_save(methodsMap, "../figures/studyLocations.tiff",
          dpi= 1000,
          units = "cm",
          width = 18,
          height = 10)

saveRDS(methodsMap, "../figures/studyLocation.RDS")
```

@@

![Schematic workflow followed in this paper. Sub-index A is calculated using spatially explicit aggregation (i.e .a simple overlay taking the mean value).](../images/workflow.jpg){#fig-workflow}

We chose three municipalities in Norway to test out the indicator @fig-studyLocation.
These municipalities are spread over xxx km north to south, and also differ in the amount of mire area, the total area surveyed, and the prevalence of infrastructure (TABLE)

```{r fig-studyLocation}
#| eval: true
#| include: true 
#| out.width: '100%'
#| fig.cap: 
#| - "Postion of the three example municipalities in
#| Norway. For each municipality the map shows ocean in blue and non-ocean 
#| in green. The survey coverage maps are in grey, and the mapped mires are 
#| in red, with polygon borderes made extra thich to make them visible, 
#| but then also exagerating their size."

(temp <- readRDS("../figures/studyLocation.RDS"))
```
